Post-Disturbance Tree Community Trajectories in a Neotropical Forest

### 2019-09-25 WholePlotTrajectories.Rmd
Rm

---
title: "Post-Disturbance Tree Community Trajectories in a Neotropical Forest"
author:
  - name: Ariane MIRABEL
    authsuperscript: 1*
  - name: Bruno Herault
    authsuperscript: 2
  - name: Eric Marcon
    authsuperscript: 1
affiliation:
  - affsuperscript: 1
    dptuniv: UMR EcoFoG, AgroParistech, CNRS, Cirad, INRA, Université des Antilles, Université de Guyane.
    address: >
      Campus Agronomique,
      97310 Kourou,
      France.
  - affsuperscript: 2
    dptuniv: INPHB, Institut National Polytechnique Félix Houphoüet-Boigny
    address: >
      Yamoussoukro,
      Ivory Coast.
corrauthor:
    email: ariane.mirabel@gmail.com
    url: https://github.com/ArianeMirabel
abstract: 
 In the current global change context, it is urgent to anticipate the fate of tropical forests.
 This means understanding tree community response to disturbance and the underlying processes.
 In that respect, we aim here to clarify taxonomic and functional post-disturbance  trajectories, and determine the scope of the Intermediate Disturbance Hypothesis (IDH) that remains debated in tropical forests.
 We analyzed community trajectories following a disturbance gradient in a Neotropical forest over 30 years. 
 We considered trajectories along time of community taxonomic and functional trajectories in terms of richness, evenness, composition, and redundancy.
 We based on the annual botanical inventories of 75 ha of a Neotropical forest and on large trait datasets comprising seven leaf, stem, and life-history traits. 
 We identified a decoupling between taxonomic composition, differing among communities, and functional composition, remaining similar and convergent. 
 The taxonomic diversity followed humped-shaped trajectories depending on the disturbance intensity, which validated the IDH (Intermediate Disturbance Hypothesis).
 The functional diversity trajectories,however, were homogeneous among all plots and dismissed the IDH.
 We explained this decoupling by the variations in community functional redundancy that mitigated the functional impact of disturbance. 
 Although consistent, the recovery of community composition, diversity, and redundancy remained unachieved after 30 years. These results acknowledged the need of decades-long cycles without disturbance to ensure community complete recovery, and questioned community resilience after repeated disturbances.
keywords: [Community Ecology, Disturbance Trajectories, Intermediate Disturbance Hypothesis, Mid-term Resilience, Neotropical Forests, Taxonomic and Functional Biodiversity]
preamble: >
  \usepackage{textcomp}
  \usepackage{tabu}
  \usepackage{caption}
  \captionsetup{justification = justified}
  \renewenvironment{table}{\begin{table*}}{\end{table*}\ignorespacesafterend}
  \hyphenation{bio-di-ver-si-ty sap-lings re-or-gan-i-za-tion post-dis-tur-bance dis-tur-bance}
  \usepackage[left]{lineno}
  \linenumbers
bibliography: references.bib
lang: english
keywordlabel: Keywords
corrauthorlabel: Corresponding author
output:
  bookdown::word_document2: default
  bookdown::pdf_book:
    base_format: EcoFoG::article
    keep_tex: TRUE
  bookdown::gitbook: default
---

>>>>

---
title: "Post-Disturbance Tree Community Trajectories in a Neotropical Forest"
author:
  - name: Ariane MIRABEL
    authsuperscript: 1*
  - name: Bruno Herault
    authsuperscript: 2
  - name: Eric Marcon
    authsuperscript: 1
affiliation:
  - affsuperscript: 1
    dptuniv: UMR EcoFoG, AgroParistech, CNRS, Cirad, INRA, Université des Antilles, Université de Guyane.
    address: >
      Campus Agronomique,
      97310 Kourou,
      France.
  - affsuperscript: 2
    dptuniv: INPHB, Institut National Polytechnique Félix Houphoüet-Boigny
    address: >
      Yamoussoukro,
      Ivory Coast.
corrauthor:
    email: ariane.mirabel@gmail.com
    url: https://github.com/ArianeMirabel
abstract: 
 In the current global change context, it is urgent to anticipate the fate of tropical forests.
 This means understanding tree community response to disturbance and the underlying processes.
 In that respect, we aim here to clarify taxonomic and functional post-disturbance  trajectories, and determine the scope of the Intermediate Disturbance Hypothesis (IDH) that remains debated in tropical forests.
 We analyzed community trajectories following a disturbance gradient in a Neotropical forest over 30 years. 
 We considered trajectories along time of community taxonomic and functional trajectories in terms of richness, evenness, composition, and redundancy.
 We based on the annual botanical inventories of 75 ha of a Neotropical forest and on large trait datasets comprising seven leaf, stem, and life-history traits. 
 We identified a decoupling between taxonomic composition, differing among communities, and functional composition, remaining similar and convergent. 
 The taxonomic diversity followed humped-shaped trajectories depending on the disturbance intensity, which validated the IDH (Intermediate Disturbance Hypothesis).
 The functional diversity trajectories,however, were homogeneous among all plots and dismissed the IDH.
 We explained this decoupling by the variations in community functional redundancy that mitigated the functional impact of disturbance. 
 Although consistent, the recovery of community composition, diversity, and redundancy remained unachieved after 30 years. These results acknowledged the need of decades-long cycles without disturbance to ensure community complete recovery, and questioned community resilience after repeated disturbances.
keywords: [Community Ecology, Disturbance Trajectories, Intermediate Disturbance Hypothesis, Mid-term Resilience, Neotropical Forests, Taxonomic and Functional Biodiversity]
preamble: >
  \usepackage{textcomp}
  \usepackage{tabu}
  \usepackage{caption}
  \captionsetup{justification = justified}
  \renewenvironment{table}{\begin{table*}}{\end{table*}\ignorespacesafterend}
  \hyphenation{bio-di-ver-si-ty sap-lings re-or-gan-i-za-tion post-dis-tur-bance dis-tur-bance}
  \usepackage[left]{lineno}
  \linenumbers
bibliography: references.bib
lang: english
keywordlabel: Keywords
corrauthorlabel: Corresponding author
output:
  bookdown::pdf_book:
    base_format: EcoFoG::article
    keep_tex: TRUE
  bookdown::word_document2: default
  bookdown::gitbook: default
---
